Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add more OP qualitative results to paper

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.  We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.

@@

Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation. Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections. As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.

@@

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7?) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work? One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks. This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos and yield more reliable, detailed detections.  A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint. Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending]. We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.

>>>>

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.

@@

Next, we examined the degree to which the detector confidence changed model performance. We found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Overall, our analyses suggested that including all detections was the most beneficial for optimizing precision; see Appendix for a full ROC curve detailing all detector confidence confidence thresholds.

Finally, we examined whether model accuracy for hands and faces varied across age or between child and location  (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}, and location in Figure \ref{fig:det_perf_by_locations}). Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points.  In general, however, we found evidence for considerable variation in model accuracy across different videos, suggesting that particular recording contexts, activities, or lighting could cause conditions that would impair detector performance.

In a qualitative analysis, we also inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance. Figure \ref{fig:error_examples} shows examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos. Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions. False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera. Hands were often missed when they were seen only from the side and unconnected to a pose, whereas hands were sometimes erroneously detected when a pose was present but the hands were out of view. Thus, while OpenPose was trained on photographs from the adult perspective, this model still performed relatively well on these challenging the egocentric infant viewpoint with no fine-tuning or post-processing of the detections, especially given these challenging and varied videos.

@@

An analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations (see Appendix, Figure S7) and between individual children. 
Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. 
This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. 
Each of these positions offer the child differing degrees of visual access to faces and hands. 
While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

So, how might OpenPose -- or other pose detection algorithms -- be improved upon and used in future work? One promising direction may be to use detailed pose annotations of the people in the infant view to fine-tune later layers of pose detection networks. This has the potential to improve upon the overall accuracy of the network to detect the social information in infant egocentric videos. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors. A second potential area for innovation lies in leveraging the dense nature of these large-scale annotations to improve model accuracy: By pooling detections from surrounding frames, we may be able to build classifiers that perform more accurately on a single challenging viewpoint. Finally, a third area for improvement consists of building classifiers that can accurately distinguish between children's hands (as seen from the egocentric point of view) versus adults' hands--a notoriously challenging problem in computer vision [@bambach2017lending]. We expect that these goals may become more and more feasible as we simultaneously improve the head-mounted cameras that are used in both at-home and in-lab studies; increasing the resolution and quality of the images we record will no doubt improve the ability of computer vision algorithms to extract detailed information from them.
